\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}

\title{Yarib Israel Nevarez Esparza \\ List of Scientific Publications}
\author{}
\date{\today}

\begin{document}

\maketitle

\begin{enumerate}
	
	\subsection*{Journal Articles}
	
	\item \textbf{Yarib Nevarez}, David Rotermund, Klaus R Pawelzik, and Alberto Garcia-Ortiz, "Accelerating Spike-by-Spike Neural Networks on FPGA With Hybrid Custom Floating-Point and Logarithmic Dot-Product Approximation," 
	\newblock IEEE Access, vol. 9, pp. 80603--80620, May 2021, doi: 10.1109/ACCESS.2021.3085216.  
	
	\item \textbf{Yarib Nevarez}, Andreas Beering, Amir Najafi, Ardalan Najafi, Wanli Yu, Yizhi Chen, Karl-Ludwig Krieger, and Alberto Garcia-Ortiz, "CNN Sensor Analytics With Hybrid-Float6 Quantization on Low-Power Embedded FPGAs," 
	\newblock IEEE Access, vol. 11, pp. 4852--4868, January 2023, doi: 10.1109/ACCESS.2023.3235866.
	
	
	\subsection*{Conference Proceedings}
	
	\item \textbf{Yarib Nevarez}, Alberto Garcia-Ortiz, David Rotermund, and Klaus R Pawelzik, "Accelerator framework of spike-by-spike neural networks for inference and incremental learning in embedded systems,"
	\newblock 2020 9th International Conference on Modern Circuits and Systems Technologies (MOCAST), Bremen, 2020, pp. 1--5, doi: 10.1109/MOCAST49295.2020.9200288.
	
	\item Wanli Yu, Ardalan Najafi, \textbf{Yarib Nevarez}, Yanqiu Huang and Alberto Garcia-Ortiz, "TAAC: Task Allocation Meets Approximate Computing for Internet of Things," 
	\newblock 2020 IEEE International Symposium on Circuits and Systems (ISCAS), Sevilla, 2020, pp. 1-5, doi: 10.1109/ISCAS45731.2020.9180895.
	
	\item Amir Najafi, Ardalan Najafi, \textbf{Yarib Nevarez} and Alberto Garcia-Ortiz, "Learning-Based On-Chip Parallel Interconnect Delay Estimation," 
	\newblock 2022 11th International Conference on Modern Circuits and Systems Technologies (MOCAST), Bremen, 2022, pp. 1--5, doi: 10.1109/MOCAST49295.2020.9200288.
	
	\item Yizhi Chen, \textbf{Yarib Nevarez}, Zhonghai Lu, and Alberto Garcia-Ortiz, "Accelerating Non-Negative Matrix Factorization on Embedded FPGA with Hybrid Logarithmic Dot-Product Approximation," 
	\newblock 2022 IEEE 15th International Symposium on Embedded Multicore/Many-core Systems-on-Chip (MCSoC), Malaysia, 2022, pp. 239--246, doi: 10.1109/MCSoC57363.2022.00070.
	
	\item Ardalan Najafi, Wanli Yu, \textbf{Yarib Nevarez}, Amir Najafi, Andreas Beering, Karl-Ludwig Krieger, and Alberto Garcia-Ortiz, "Acoustic Emission Source Localization using Approximate Discrete Wavelet Transform," \newblock 2023 12th International Conference on Modern Circuits and Systems Technologies (MOCAST), Bremen, 2023, pp. 1--5, doi: 10.1109/MOCAST57943.2023.10176952.
	
\end{enumerate}


\end{document}

