\section{Project plan}
This PhD is divided into three phases that are subdivided into tasks. The prospective milestone schedule is shown in \Tab{tab:mileston_schedule}. The total timeframe is expected to be 3 years.

\subsection{Phase 1 (completed)}
\begin{enumerate}
\item Research of hardware design methodologies for custom neural network accelerators in embedded FPGA.
\item Design and implementation of an scalable neural network accelerator framework for design exploration.
\item Implement an spiking neural network model using the accelerator framework.
\item Report experimental results in a conference publication.
\end{enumerate}

\subsection{Phase 2 (completed)}
\begin{enumerate}
	\item Investigate error resilience of the SNN (Spike-by-Spike neural network).
	\item Derive approximate computing methodology to exploit the error resilience of the SNN.
	\item Implement the approximate computing approach on the neural network accelerator framework on FPGA.
	\item Report approximate computing approach, methodology, and experimental results in a journal publication.
\end{enumerate}

\subsection{Phase 3}
\begin{enumerate}
	\item Extend the design exploration framework to support deep CNN.
	\item Extend the design exploration framework to support CNN-based multiple object detection for computer vision.
	\item Implement an state-of-the-art multiple object detection algorithm on FPGA (e.g., YOLOv4 \cite{bochkovskiy2020yolov4}).
	\item Investigate error resilience analysis of CNN-based detection algorithm.
	\item Implement hardware accelerator with the proposed approximate computing approach and design methodology.
	\item Report approximate computing approach, methodology, and experimental results in a journal publication.
\end{enumerate}

\subsection{Phase 4}
\begin{enumerate}
\item PhD thesis writing.
\end{enumerate}
	
	\begin{longtable}{|l|l|m{9cm}|}
		\hline
		\rowcolor[HTML]{C0C0C0} 
		\textbf{Milestone} & \textbf{Date}   & \textbf{Description}                                                                                                                                                                                                                                                                                                                                                                                                                                                                \\ \hline
		M1                 & September, 2019 & Completion of literature search                                                                                                                                                                                                                                                                                                                                                                                                                                                     \\ \hline
		M2                 & January, 2020   & Understand the key design considerations for efficient ML processing; understand trade-offs between various hardware architectures and platforms; learn about micro-architectural knobs such as precision, data reuse, and parallelism to architect ML accelerators given target area-power-performance metrics; evaluate the utility of various ML dataflow techniques for efficient processing; and understand future trends and opportunities of approximate neural network accelerators \\ \hline
		M3                 & April, 2020     & Outcome: Development of an accelerator framework of Spike-By-Spike (SbS) neural networks for inference and incremental learning in FPGA. Report results in a conference publication \cite{nevarez2020accelerator}                                                                                                                                                                                                                                                                                                                                                                     \\ \hline
		M4                 & July, 2020      & Investigate error resilience analysis of SbS neural network algorithm                                                                                                                                                                                                                                                                           \\ \hline
		M5                 & October, 2020   & Investigate and simulate approximate computing methodologies on SbS neural networks as a case study                                                                                                                                                                                                                             \\ \hline
		M6                 & January, 2021   & Report methodology and results of the case study in a journal publication
		\\ \hline
		M7                 & April, 2021     & Outcome: Extend the neural network accelerator framework to support deep CNN, and CNN-based multiple object detector algorithms for computer vision                                                                                                                                                                                                                                                                                                                       \\ \hline
		M8                 & July, 2021      & Investigate error resilience in CNN-based algorithms                                                                                                                                                                                                                                                                                                                                        \\ \hline
		M9                 & October, 2021   & Outcome: Report results of methodology in a journal publication                                                                                                                                                                                                                                                                                                                                                                                          \\ \hline
		M10                & Jun, 2022       & Written elaboration is completed                                                                                                                                                                                                                                                                                                                                                                                                                                                    \\ \hline
		\caption{Milestone schedule.}\label{tab:mileston_schedule}
	\end{longtable}
%\end{table}