\section{Project plan}
The research project will be divided into three phases, the prospective milestones schedule is shown in \Tab{tab:mileston_schedule}. The total timeframe is expected to be 3 years.

\subsection{Phase 1}
In-depth research of existing work. Existing findings should be incorporated into the own work effectively. For this purpose, a trial and evaluation of existing analysis and design tools. The goal of Phase 1 is to develop first FPGA-based prototypes compatible with the requirements of Industry 4.0 devices.

Outcome: First, it will result in a library of IP-blocks and hardware architectures consisting on prior state of the art. Second, it will result in a quantitative evaluation of existing techniques as well as the identification of the most relevant bottlenecks in previous approaches. The library of IP-block is expected to be open-sourced and the quantitative analysis reported in a journal paper.

\subsection{Phase 2}
Selection of suitable design tools as well as a strategy for the further improvements in performance and real-time characteristics. In particular stochastic and approximation techniques in hardware acceleration will be considered. Investigations on feature extraction, ML approximations, and acceleration approaches in configurable logic and hardware. Development of a second prototype based on the automated design flow. The second prototype has a higher computing capabilities.

Outcome: Improved FPGA prototype that demonstrates in real Industry 4.0 applications the advantages of the proposed architecture.

\subsection{Phase 3}
Selection of final approach, strategies, and hardware architectures for the final project phase. Development of an optimized System-on-Chip architecture with resource constrained embedded devices that efficiently execute real-time machine leaning algorithms in IIoT applications. The research will be documented and published in written form.

Outcome: Development of a SoC in a nanometric technology using the architecture proposed in phase 2.


%\begin{table}[t!]
	
	\begin{longtable}{|l|l|m{9cm}|}
		\hline
		\rowcolor[HTML]{C0C0C0} 
		\textbf{Milestone} & \textbf{Date}   & \textbf{Description}                                                                                                                                                                                                                                                                                                                                                                                                                                                                \\ \hline
		M1                 & September, 2019 & Completion of literature search                                                                                                                                                                                                                                                                                                                                                                                                                                                     \\ \hline
		M2                 & January, 2020   & Understand the key design considerations for efficient ML processing; understand trade-offs between various hardware architectures and platforms; learn about micro-architectural knobs such as precision, data reuse, and parallelism to architect ML accelerators given target area-power-performance metrics; evaluate the utility of various ML dataflow techniques for efficient processing; and understand future trends and opportunities from ML algorithms on Industry 4.0 \\ \hline
		M3                 & April, 2020     & Outcome: Development of a library of IP-blocks and hardware architectures consisting of prior state of the art                                                                                                                                                                                                                                                                                                                                                                      \\ \hline
		M4                 & July, 2020      & Outcome: Quantitative evaluation of existing techniques as well as the identification of the most relevant bottlenecks in previous approaches, report in a journal paper                                                                                                                                                                                                                                                                                                            \\ \hline
		M5                 & October, 2020   & Selection of tools, strategies, techniques for further improvements in performance and real-time characteristics. Stochastic and approximation techniques in hardware acceleration                                                                                                                                                                                                                                                                                                  \\ \hline
		M6                 & January, 2021   & Investigations on feature extraction, ML approximations, and acceleration approaches in configurable logic and hardware                                                                                                                                                                                                                                                                                                                                                             \\ \hline
		M7                 & April, 2021     & Outcome: Improved FPGA prototype that demonstrates in real Industry 4.0 applications the advantages of the proposed architecture                                                                                                                                                                                                                                                                                                                                                    \\ \hline
		M8                 & July, 2021      & Development of SoC architecture efficiently executing real-time machine leaning algorithms in IIoT is completed                                                                                                                                                                                                                                                                                                                                                                     \\ \hline
		M9                 & October, 2021   & Development of a SoC in a nanometric technology is completed                                                                                                                                                                                                                                                                                                                                                                                                                        \\ \hline
		M10                & Jun, 2022       & Written elaboration is completed                                                                                                                                                                                                                                                                                                                                                                                                                                                    \\ \hline
		\caption{Milestone schedule.}\label{tab:mileston_schedule}
	\end{longtable}
%\end{table}