\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{titlesec} % For title spacing adjustment

\geometry{left=1in, top=1in, right=1in, bottom=1in} % Adjust margins
\setlist{nosep} % Reduces space in itemize
\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{1em}{} % Adjusts section spacing
\titlespacing*{\section}{0pt}{5pt}{5pt} % Reduces space around sections

\title{Yarib Israel Nevarez Esparza \\ Life and Educational Path}
\author{}
\date{\today}

\begin{document}
	
	\maketitle
	\vspace{-10mm} % Reduces space after title
	
	\section*{Early Life and Education}
	\begin{itemize}
    \item \textbf{Birthplace:} Durango City, northern Mexico.
    \item \textbf{Early interests:} Passion for electronics and mathematics since childhood; curiosity led to building electronic circuits.
    \item \textbf{Secondary school (1998-2001):} Participation winning in electronics creativity contests.
    \item \textbf{High school (2001-2004):} Majored as a technician in electronics, won multiple contests in mathematics, physics, and electronics.
    \item \textbf{Hobbies:} Building electronic circuits and computer programming with C/C++.
\end{itemize}

\section*{University Education}
\begin{itemize}[noitemsep]
    \item \textbf{Bachelor's degree (2004-2008):} Electronics at Durango Institute of Technology. Continued success winning in academic contests across various subjects (mathematics, physics, electronics, and creativity). 
    \item \textbf{Leadership roles:} Vice president of the IEEE student branch; represented the institute in Latin-American student leader conferences.
    \item \textbf{Hobbies:} Continued interest in C/C++ programming, focusing on microcontrollers.
\end{itemize}

\section*{Professional Career}
\begin{itemize}[noitemsep]
    \item \textbf{Initial career (2009):} Embedded software engineer at Texas Instruments in Aguascalientes, Mexico. Developed software for graphics calculators and advanced to a senior engineer position in short time (two and a half years).
    \item \textbf{Further career moves:} Positions in IBM, Continental Automotive, and Toshiba in Guadalajara City, Mexico.
\end{itemize}

\section*{Advanced Studies and Career in Germany}
\begin{itemize}[noitemsep]
    \item \textbf{Master of Science in Embedded Systems Design (2016):} After one semester at the Technical University of Jena, Germany; transitioned to Embedded Systems Design at the Technical University of Bremerhaven.
    \item \textbf{Industry experience:} Master thesis intern at E.I.S. Electronics GmbH, developing an FPGA-based controller system for airplanes.
    \item \textbf{Doctoral studies (started May 2019):} At the University of Bremen's Institute for Theoretical Electrical Engineering and Microelectronics (ITEM) under Prof. Dr.-Ing. Alberto García-Ortiz.
    \item \textbf{Research focus:} Investigating neural network accelerators for low-power embedded systems. Funded by CONACYT.
\end{itemize}

\section*{Current Status}
\begin{itemize}[noitemsep]
    \item \textbf{Post-Doctoral researcher (started June 2022):} Working at NXP Semiconductors in the Netherlands on a Long Term Innovation project in the CTO division.
    \item \textbf{Research area:} Strong neural network quantization, custom floating-point, and novel on-device learning approaches for resource-constrained embedded applications (tinyML).
\end{itemize}

\end{document}

